MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-01-27 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
fix typo

# Store correlation between tissues
write.table(correlation_tissue, file = 'CMC_ACC_DLPFC_correlationTissue.tsv', sep = '\t', row.names = FALSE, quote = FALSE)
COR_OBJ = File('CMC_ACC_DLPC_correlationTissue.tsv',
               name = 'Correlation between Tissues, Same Individual',
               parentId = CODE$properties$id)
COR_OBJ = synStore(COR_OBJ, used = ALL_USED_IDs, activityName = activityName,
                   executed = thisFile, activityDescription = acactivityDescription)
synSetAnnotations(COR_OBJ, annotations = all.annotations)
```
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Residual Expression (for network analysis) |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |
|  Enrichment Analysis                        |  `r ENRICH_OBJ$properties$id`    |

>>>>

# Store correlation between tissues
write.table(correlation_tissue, file = 'CMC_ACC_DLPFC_correlationTissue.tsv', sep = '\t', row.names = FALSE, quote = FALSE)
COR_OBJ = File('CMC_ACC_DLPC_correlationTissue.tsv',
               name = 'Correlation between Tissues, Same Individual',
               parentId = CODE$properties$id)
COR_OBJ = synStore(COR_OBJ, used = ALL_USED_IDs, activityName = activityName,
                   executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(COR_OBJ, annotations = all.annotations)
```
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Residual Expression (for network analysis) |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |
|  Enrichment Analysis                        |  `r ENRICH_OBJ$properties$id`    |
